Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-07-24 algorithm.tex
AA: arrivato fino a prima di termination condition. Ma ancora servono altre iterazioni nella parte precedente

\section{The algorithm}
\label{sec:algorithm}

The algorithm we present is iterative. Each iteration is called \emph{era}.

Each era $era_{i}$ is characterized by 
\begin{itemize}
\item the set of regions $\mathcal{R}_{i}$ in which the parameter space
$P_{1}\times\dots\times P_{n}$ is divided
\item its Pareto set $\mathscr{P}_{i}$
\item a set $test_{i}$ of at most $K$ configurations to evaluate
\end{itemize}
$K$ is a parameter that must be set before the algorithm runs.

\subsection{Start Condition}
$\mathcal{R}_{0}=\left\{ P_{1}\times\dots\times P_{n}\right\} $,
i.e. era $0$ has only one region that is the whole parameter space.
A random set $test_{0}$ of $K$ configurations is evaluated. The
Pareto set $\mathscr{P}_{0}=\mathscr{P}\left(test_{0}\right)$ is
calculated (see def \ref{pers02.def:Pareto-set} for the definition
of the operator $\mathscr{P}_{i}$ over a set)

\subsection{Iteration Rules}

For $era_{i}$ with $i>0$ the following operations must be performed.
\begin{enumerate}
\item \label{pers02.enu:K}For each region $R\in\mathcal{R}_{i}$, a set
$test_{R,i}$ of configurations is randomly chosen in%
\footnote{Therefore the chosen configurations can only be configurations of
$R$ not yet evaluated in past eras.%
} $R\setminus\bigcup_{j=0}^{i-1}test_{j}$. The number of configurations
in $test_{R,i}$ is set to%
\footnote{This means that $\frac{K}{\left|\mathcal{R}_{i}\right|}$ configurations
are to be chosen, but if not yet evaluated configurations in $R$
are less then $\frac{K}{\left|\mathcal{R}_{i}\right|}$, all of them
are chosen%
} 
\[
\min\left(\frac{K}{\left|\mathcal{R}_{i}\right|},\left|R\setminus\bigcup_{j=1}^{i-1}test_{j}\right|\right)
\]
The set 
\[
test_{i}=\bigcup_{R\in\mathcal{R}_{i}}test_{R,i}
\]
 is defined. 
\item All configurations on $test_{i}$ are simulated.
\item The Pareto set $\mathscr{P}_{i}$ for $era_{i}$ is defined as 
\[
\mathscr{P}_{i}=\mathscr{P}\left(test_{i}\cup\mathscr{P}_{i-1}\right)
\]

\item \label{pers02.enu:novelty_score_of_a_configuration}Every point $\mathbf{p}$
of%
\footnote{The innovation score is not given to those points in $test_{i}$ that
are not in the Pareto set%
} $test_{i}\cap\mathscr{P}_{i}$ is given an \emph{innovation score
}defined as:
\[
is\left(\mathbf{p}\right)=\min\left\{ \left.s\left(\mathbf{q}\rightarrow\mathbf{o}\left(\mathbf{p}\right)\right)\right|\mathbf{q}\in\mathscr{P}_{i-1}\right\} 
\]
 (a configuration $\mathbf{p}$ is characterized by as much innovation
as more separated it is from the configurations of the previous era)\@.
\item Every region $R\in\mathcal{R}_{i}$ is given an innovation score defined
as:
\[
is\left(R\right)=\sum\left\{ \left.is\left(\mathbf{p}\right)\right|\mathbf{p}\in\mathscr{P}_{i}\cap R\right\} 
\]

\item The total innovation score for the entire era is:
\[
is_{TOT,i}=\sum_{R\in\mathcal{R}_{i}}is\left(R\right)
\]

\item The average innovation score for the entire era is also calculated
as:
\[
is_{av,i}=\frac{is_{TOT,i}}{\left|\mathcal{R}_{i}\right|}
\]
where $\left|\mathcal{R}_{i}\right|$ is the number of regions of
era $i$ .
\item $\mathcal{R}_{i}$ is partitioned in three subsets (their meaning
will be discussed later):

\begin{enumerate}
\item high innovation regions 
\[
\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i-1}\right\} 
\]
 where $\alpha$ is a constant defined by the designer (for example
$\alpha=1.2$). Each $R\in\mathcal{R}_{i,h}$ is split in $\mathcal{R}^{R}$
(as stated in def \ref{pers02.def:Splitting-a-region})
\item low innovation regions 
\[
\mathcal{R}_{i,l}=\left\{ \left.R\in\mathcal{R}_{i}\right|0<is\left(R\right)\le\alpha\cdot is_{av,i-1}\right\} 
\]
They are not changed.
\item no innovation regions 
\[
\mathcal{R}_{i,n}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)=0\right\} 
\]
\end{enumerate}

\item Disjoint couples of contiguous regions $\left(R_{1},R_{2}\right)$,
with $R_{1},R_{2}\in\mathcal{R}_{i,n}$ are selected. The set of this
couples is indicated as $\mathcal{C}$. The couples of regions are
merged:
\[
\forall\left(R_{1},R_{2}\right)\in\mathcal{C}\Rightarrow R=R_{1}+R_{2}
\]
 (see def \ref{pers02.def:Merging-regions})
\item The set of regions $\mathcal{R}_{i+1}$ for the following era is defined
as:
\[
\mathcal{R}_{i+1}=
\]
\[
=\left(\bigcup_{R\in\mathcal{R}_{i,h}}\mathcal{R}^{R}\right)\cup\mathcal{R}_{i,l}\cup
\]
\[
\cup\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup
\]
\[
\cup\left(\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left(R_{1}+R_{2}\right)\right)
\]

\end{enumerate}

@@

>>>>

\section{The algorithm}
\label{sec:algorithm}
\comment{Mettiamo PS algorithm come titolo della sezione almeno rinforziamo nella memoria il suo nome?}
In this section we present PS, the algorithm that we propose to perform the Design Space Exploration (DSE). As any other DSE algorithm, its input is the parameterized system $S$ and a benchmark application $b$, while the output is an approximation of the Pareto-optimal set $\mathcal{P}\left(S,b\right)$. \comment{E' corretto?}  
PS is iterative and we will describe, separately, the initialization phase, the operations performed inside each iteration and the condition that triggers the termination.

By a slightly abuse of notation, considering a subset $I$ of the configuration space, we will denote with $\mathcal{P}(I,b)$ the non-dominated feasible configurations in $I$, i.e.
	\begin{align}
		\mathcal{P}(I,b)=
		\left\{ \mathbf{c} \in I \cap \mathcal{C}^*(S) | \nexists \ \mathbf{c}' \in I \cap \mathcal{C}^*(S), \mathbf{c}' \succ \mathbf{c} \right\}
	\end{align}
Since in each run of the algorithm we will consider only one benchmark application $b\in\mathcal{B}$, we will omit it, replacing, for example, $\mathcal{P}(I,b)$ with  $\mathcal{P}(I)$.

Each iteration is called \emph{era}. The $i$-th era is characterized by: 
	\begin{itemize}
	\item the set of regions $\mathcal{R}_{i}$ in which the configuration space
	$mathcal{C}(S)=V_{1}\times\dots\times V_{n}$ is partitioned
	\item an approximation $\mathscr{P}_{i}$ of the Pareto-optimal set.
	\item a set $test_{i}$ of at most $K$ configurations evaluated in the era. \comment{Nella era i o nella successiva?}
	\end{itemize}
$K$ is a parameter that must be set before the algorithm runs. \comment{Spiegare un po' l'impatto di K.} Note that $\mathcal{R}_{i}$ is a partition of the configuration space, i.e.
	\begin{align}\begin{array}{l}
		\bigcup_{R\in\mathcal{R}_i} R = \mathcal{C}(S) \mbox{ and}\\
		R' \cap R'' = \emptyset, \forall R',R'' \in \mathcal{R}_i
	\end{array}\end{align}

\comment{Prima di sbattere tutta la sfilza di steps, dovremmo dare un'idea preliminare di cosa si andra' a fare.}

\subsection{Initialization}
We fix $\mathcal{R}_0$, $\mathscr{P}_0$ and $test_0$ for the era $0$ as follows. Era $0$ has only one region that is the whole parameter space,
i.e. $\mathcal{R}_{0}=\left\{ V_{1}\times\dots\times V_{n}\right\} $.
A random set $test_{0}$ of $K$ configurations is evaluated. The
Pareto set $\mathscr{P}_{0}=\mathscr{P}\left(test_{0}\right)$ is
calculated.

\subsection{Iteration steps}

For $era_{i}$ with $i>0$ the following operations must be performed.
\begin{enumerate}
\item \label{pers02.enu:K}
In each era $i$, a set $test_i$ of $K$ configurations will be evaluated. We call them \emph{test configurations} and selecting them is exactly the goal of this step.
We select only \emph{new} configurations, i.e. the ones that have not been evaluated in past eras. In other words, $test_i$ must not contain $\bigcup_{j=0}^{i-1}test_{j}$.
Since all regions $R$ in the configuration space partition $\mathcal{R}_{i}$ must be properly explored, we have to distribute the test configurations among all these regions. For this reason, $\frac{K}{\left|\mathcal{R}_{i}\right|}$ configurations are randomly extracted from the new configurations of each region $R\in\mathcal{R}_{i}$. We denote the set of the selected configurations with $test_{R,i}$ and, obviously, $\bigcup_{R\in\mathcal{R}_{i}} test_{R,i} = test_i$.
 In case the new configurations in $R$ are less then $\frac{K}{\left|\mathcal{R}_{i}\right|}$, all of them are selected. In this case $test_{R,i}=R\setminus\bigcup_{j=0}^{i-1}test_{j}$, where  $\bigcup_{j=0}^{i-1}test_{j}$ is the set of the configurations already in the past.\footnote{Note that if such regions exist, the total number of evaluations in era $i$ will be less than $K$}
\item All configurations on $test_{i}$ are simulated.
\item The Pareto set $\mathscr{P}_{i}$ for $era_{i}$ is defined as the set of non-dominated configurations among the ones evaluated so far, i.e.
	\[
	\mathscr{P}_{i} \triangleq
	\mathscr{P}\left(\bigcup_{j\leq i}test_j\right)=
	\mathscr{P}\left(test_{i}\cup\mathscr{P}_{i-1}\right)
	\]
where the last equality can easily be proved.

\item \label{pers02.enu:novelty_score_of_a_configuration}
The test configurations that are dominated, i.e. do not belong to $\mathscr{P}_i$, are neglected, while an \emph{innovation score} is given to the other ones, computed on the base of their separation from the non-dominated configurations of the past eras. Recalling that $s$ is the separation (see \defR{separation}), the innovation score of a non-dominated test configuration $\mathbf{c}^*$ is defined as
	\[
	is\left(\mathbf{c}^*\right)=\min\left\{ \left.s\left(\mathbf{c}\rightarrow\mathbf{c} \right)\right|\mathbf{c}\in\mathscr{P}_{i-1}\right\} 
	\]
In other words, a configuration $\mathbf{c}^*$ is characterized by as much innovation
as more separated it is from the configurations of the previous era.

\item Every region $R\in\mathcal{R}_{i}$ is given an innovation score defined
as the sum of the innovation scores of its non-dominated test configurations:
	\[
	is\left(R\right)=\sum\left\{ \left.is\left(\mathbf{c}\right)\right|\mathbf{c}\in\mathscr{P}_{i}\cap R\right\} 
	\]

\item The total innovation and average score for the entire era is calculated:
	\[
	is_{TOT,i}=\sum_{R\in\mathcal{R}_{i}}is\left(R\right)
	\]

\item The configuration space partition $\mathcal{R}_{i}$ is divided in three subsets, that we will comment later \comment{e invece sarebbe bene commentarli ora, anche}:

	\begin{enumerate}
	\item high innovation regions 
	\[
	\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i-1}\right\} 
	\]
	 where $\alpha$ is a constant defined by the designer (for example
	$\alpha=1.2$). 
	\item low innovation regions 
	\[
	\mathcal{R}_{i,l}=\left\{ \left.R\in\mathcal{R}_{i}\right|0<is\left(R\right)\le\alpha\cdot is_{av,i-1}\right\} 
	\]
	\item no innovation regions 
	\[
	\mathcal{R}_{i,n}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)=0\right\} 
	\]
	\end{enumerate}

\item The goal of this step is preparing the regions that will compose the configuration space partition of the next era, i.e. $\mathscr{R}_{i+1}$. The following operations are performed:
	\begin{enumerate}
		\item Each high innovation region $R\in\mathscr{R}_{i,h}$ is split obtaining $\psi(R)$, as stated in def \defR{splitting-a-region}. We denote with $\psi\left(\mathscr{R}_{i,h}\right)$ the set of regions obtained as explained.
		\item Low innovation regions are left unchanged.
		\item No innovation regions are merged, two by two. To do so, couples of no innovation contiguous regions $(R_1,R_2)$ are selected. We denote the set of these couples as $\mathscr{M}_i$. This set is constructed such that couples are independent, i.e. there cannot be two of them sharing a region. In other words, taking whatever $(R_1,R_2),(R_3,R_4) \in \mathscr{M}_i$, $R_i \neq R_j, \forall i,j\in\lbrace1,2,3,4\rbrace, i\neq$. 
We merge each couple of regions, i.e. $\forall (R_1,R_2)\in\mathscr{M}_i$ we calculate $\mu(R_1,R_2)$, according to \defR{merging-regions}.
We stress that the regions that belong to each selected couple must be contiguous, otherwise it is impossible to merge them. We denote with $\mu(\mathscr{M}_i)$ the set of the merged regions, i.e. $\mu(\mathscr{M}_i) = \bigcup_{(R_1,R_2)\in\mathscr{M}_i} \mu(R_1,R_2)$
	\end{enumerate}

\item The set of regions $\mathcal{R}_{i+1}$ for the following era is computed as:
	\[
	\mathcal{R}_{i+1}=
	\]
	\[
	=\psi\left(\mathscr{R}_{i,h}\right) \cup \mathcal{R}_{i,l}\cup
	\]
	\[
	\cup\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup \mu(\mathscr{M}_i)
	\]
\end{enumerate}

\comment{commentare questa formula}

\comment{SONO ARRIVATO A LEGGERE QUA}

@@

\comment{Ci vorrebbe una rappresentazione schematica dell'algoritmo usando l'ambiente latex Algorithm o non mi ricordo come si chiama}

### 2014-07-24 concepts.tex
AA: arrivato fino a prima di termination condition. Ma ancora servono altre iterazioni nella parte precedente

\comment{Theoretical suona troppo pomposo? Esportare di nuovo tutte le immagini libreoffice - svg - eps che viene meglio e aggiutare i nomi degli assi}
In this section we provide the concepts and the formal definitions that we will use later to express our algorithm. \comment{Ha un nome l'algoritmo?} First, we give the definitions of Pareto-set and Pareto-front that lie on the basis of Design Space Exploration is based on. Then, we sketch the fundamental idea behind our algorithm. Finally, we provide a formal definition of the regions, of their properties and of the operations that will be performed on them by the algorithm.

\subsection{Pareto-set and Pareto-front}
\label{sec:pareto}

@@

\begin{definition}[Pareto Set]
\label{pers02.def:Pareto-set}
The {\em Pareto-optimal set} of $S$ for the application $b$ is the
set:
\[ \mathcal{P}(S,b) = \{ \mathbf{c} \in \mathcal{C}^*(S) \ | \nexists \ \mathbf{c}' \in \mathcal{C}^*(S), \mathbf{c}' \succ \mathbf{c} \} \]
\end{definition}
that is, the set of configurations $\mathbf{c} \in
\mathcal{C}^*(S)$ not dominated by any other \comment{feasible}
 configuration.
The configurations belonging to the Pareto-optimal set are called \emph{Pareto-optimal configurations}, while the {\em Pareto-optimal front} is their image, i.e. the set:
\[ \mathcal{P}_{F}(S,b) = \{ \mathbf{o} | \mathbf{o} = E(\mathbf{c},b), \mathbf{c} \in \mathcal{P}(S,b) \} \]

@@

We now provide some rules to split and merge regions. They will be
useful when explaining our proposed exploration algorithm.
\begin{definition}[Splitting an interval]
\label{pers02.def:Splitting-a-region}
Given a $p_i$ interval $\left[a_{i}..b_{i}\right]$ with more than one element, i.e. $\left|\left[a_{i}..b_{i}\right]\right|>1$, the splitting operation produces as result two contiguous intervals $\left[a_{i}..c_{i}\right],\left[d_{i}..b_{i}\right]$
 such that
	\begin{align}
		\begin{cases}
		\left[a_{i}..c_{i}\right]\cap\left[d_{i}..b_{i}\right] & =\emptyset\\
		\left[a_{i}..c_{i}\right]\cup\left[d_{i}..b_{i}\right] & =\left[a_{i}..b_{i}\right]\\
		\left|\left[a_{i}..c_{i}\right]\right| & =\left\lceil \frac{\left|\left[a_{i}..b_{i}\right]\right|}{2}\right\rceil 
		\end{cases}
	\end{align}

@@

\begin{definition}[Merging regions]
\label{pers02.def:Merging-regions}
Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$ be two contiguous regions and let $p_j$ be the contiguity parameter. 
The merge operation $\mu$ applied to $R_1$ and $R_2$ produces a new region of the following form:
	\begin{align}
		\mu(R_1,R_2)=\prod_{i<j}\left[a_{i}..b_{i}\right]
		\times
		\mu	 \left( \begin{array}{l}
				\left[a_{j}..y_{j}\right] \\
				\left[x_{j}..b_{j}\right]
		     \end{array} \right)
		\times
		\prod_{i>j}\left[a_{i}..b_{i}\right]
	\end{align}
\end{definition}

@@

\begin{definition}[Separation]
Let $\mathbf{c}',\mathbf{c}''\in S$ be two configurations, $b\in\mathcal{B}$ a benchmark application and $\mathbf{o}',\mathbf{o}''\in \Re^m$ the representation of the configurations in the objective space, i.e. $\mathbf{o}'=E \left(\mathbf{c}', b\right)$, $\mathbf{o}''=E \left(\mathbf{c}'', b\right)$, where $E$ is the evaluation function. The separation between
$\mathbf{c}'$ and $\mathbf{c}''$ is 
	\[
	s\left(\mathbf{c}'\rightarrow\mathbf{c}''\right)=\sum_{i=1}^{m}\left|\frac{o'_{i}-o''_{i}}{o'_{i}}\right|
	\]
where $o'_i$ and $o''_i$ are the $i$-th components of $\mathbf{o}'$ and $\mathbf{o}''$, respectively.
\end{definition}

>>>>

\comment{Theoretical suona troppo pomposo? Esportare di nuovo tutte le immagini libreoffice - svg - eps che viene meglio, come si vede in \figR{3}. Aggiustare i nomi degli assi che in alcune figure sono sbagliati. O forse basta esportarli col nuovo libreoffice che fa meglio}
In this section we provide the concepts and the formal definitions that we will use later to express PS, the algorithm we propose.
 First, we give the definitions of Pareto-set and Pareto-front that lie on the basis of Design Space Exploration is based on. Then, we sketch the fundamental idea behind our algorithm. Finally, we provide a formal definition of the regions, of their properties and of the operations that will be performed on them by the algorithm.

\subsection{Pareto-set and Pareto-front}
\secL{pareto}

@@

\begin{definition}[Pareto Set]
\label{pers02.def:Pareto-set}
The {\em Pareto-optimal set} of $S$ for the application $b$ is the
set:
\[ \mathcal{P}(S,b) = \left\{ \mathbf{c} \in \mathcal{C}^*(S) \ | \nexists \ \mathbf{c}' \in \mathcal{C}^*(S), \mathbf{c}' \succ \mathbf{c} \right\} \]
\end{definition}
that is, the set of configurations $\mathbf{c} \in
\mathcal{C}^*(S)$ not dominated by any other \comment{feasible}
 configuration.
The configurations belonging to the Pareto-optimal set are called \emph{Pareto-optimal configurations}, while the {\em Pareto-optimal front} is their image, i.e. the set:
\[ \mathcal{P}_{F}(S,b) = \{ \mathbf{o} | \mathbf{o} = E(\mathbf{c},b), \mathbf{c} \in \mathcal{P}(S,b) \} \]

@@

We now provide some rules to split and merge regions. They will be
useful when explaining our proposed exploration algorithm.
\begin{definition}[Splitting an interval]
\defL{splitting-a-region}
Given a $p_i$ interval $\left[a_{i}..b_{i}\right]$ with more than one element, i.e. $\left|\left[a_{i}..b_{i}\right]\right|>1$, the splitting operation produces as result two contiguous intervals $\left[a_{i}..c_{i}\right],\left[d_{i}..b_{i}\right]$
 such that
	\begin{align}
		\begin{cases}
		\left[a_{i}..c_{i}\right]\cap\left[d_{i}..b_{i}\right] & =\emptyset\\
		\left[a_{i}..c_{i}\right]\cup\left[d_{i}..b_{i}\right] & =\left[a_{i}..b_{i}\right]\\
		\left|\left[a_{i}..c_{i}\right]\right| & =\left\lceil \frac{\left|\left[a_{i}..b_{i}\right]\right|}{2}\right\rceil 
		\end{cases}
	\end{align}

@@

\begin{definition}[Merging regions]
\defL{merging-regions}
Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$ be two contiguous regions and let $p_j$ be the contiguity parameter. 
The merge operation $\mu$ applied to $R_1$ and $R_2$ produces a new region of the following form:
	\begin{align}
		\mu(R_1,R_2)=\prod_{i<j}\left[a_{i}..b_{i}\right]
		\times
		\mu	 \left( \begin{array}{l}
				\left[a_{j}..y_{j}\right] \\
				\left[x_{j}..b_{j}\right]
		     \end{array} \right)
		\times
		\prod_{i>j}\left[a_{i}..b_{i}\right]
	\end{align}
\end{definition}

@@

\begin{definition}[Separation]
\defL{separation}
Let $\mathbf{c}',\mathbf{c}''\in \mathcal{C}^*(S)$ be two feasible \comment{e' giusto che ho messo feasible? Se considerassimo anche le unfeasible sarebbe impossibile calcolarne le immagini nell'objective space?} configurations of the system $S$, $b\in\mathcal{B}$ a benchmark application and $\mathbf{o}',\mathbf{o}''\in \Re^m$ the representation of the configurations in the objective space, i.e. $\mathbf{o}'=E \left(\mathbf{c}', b\right)$, $\mathbf{o}''=E \left(\mathbf{c}'', b\right)$, where $E$ is the evaluation function. The separation between
$\mathbf{c}'$ and $\mathbf{c}''$ is 
	\[
	s\left(\mathbf{c}'\rightarrow\mathbf{c}''\right)=\sum_{i=1}^{m}\left|\frac{o'_{i}-o''_{i}}{o'_{i}}\right|
	\]
where $o'_i$ and $o''_i$ are the $i$-th components of $\mathbf{o}'$ and $\mathbf{o}''$, respectively.
\end{definition}

### 2014-07-24 introduction.tex
AA: lavorato fino a sezione 3 ma ancora ho bisogno di farci altre iterazioni
AA: arrivato fino a prima di termination condition. Ma ancora servono altre iterazioni nella parte precedente

\section{Introduction and Motivation}

@@

In this work we present a multiobjective design exploration strategy
that introduces the concept of Parameter Space Representation of
Pareto Set (PS). The main idea is focusing on the ``innovation''
introduced in the Pareto sets and then accordingly distributing the
exploration effort in regions created in the multidimensional space of
system parameters. The aim of the PS approach is to propose a new
perspective on the configuration space, where parameter
interdependencies play the fundamental role of making some regions
more capable of generating hardly predictable solutions: catching this
sort of ``chaoticity'' in the parameter space is the main idea behind
the strategy that is being introduced in this work.

>>>>

\section{Introduction and Motivation}
\comment{Si capisce che noi provide an algorithm?}

\comment{Mettere our contribution?}

\comment{Usare triangleq quando definiamo noi le cose, per distinguerlo dall'= di calcolo}

@@

In this work we present a multiobjective design exploration strategy
that introduces the concept of Parameter Space Representation of
Pareto Set (PS).\comment{Provo a fare il reviewer stronzo. Allora, quando parliamo di parameter space, non si capisce bene di cosa parliamo. Alla fin fine penso (ma gia' se nemmeno io che ci ho messo mano ne sono sicuro, figuriamoci il reviewer) stiamo parlando del configuration space, che definiamo precisamente nella \secR{pareto}. In altre parole parameter space == configuration space. Quindi, visto che il Pareto set e' contenuto nel configuration space, il Pateto-set e' gia', lui stesso, una Parameter Space Representation of Pareto-set. E' come dire ``io sono la rappresentazione di me stesso'', che filosoficamente e' affascinante ma matematicamente non lo e' altrettanto!} The main idea is focusing on the ``innovation''
introduced in the Pareto sets and then accordingly distributing the
exploration effort in regions created in the multidimensional space of
system parameters. The aim of the PS approach is to propose a new
perspective on the configuration space, where parameter
interdependencies play the fundamental role of making some regions
more capable of generating hardly predictable solutions: catching this
sort of ``chaoticity'' in the parameter space is the main idea behind
the strategy that is being introduced in this work.

### 2014-07-24 paper.tex
AA: lavorato fino a sezione 3 ma ancora ho bisogno di farci altre iterazioni
AA: arrivato fino a prima di termination condition. Ma ancora servono altre iterazioni nella parte precedente

\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{balance}
\usepackage{float}
\usepackage{threeparttable}

@@

%------------------------------------------------------------------------------

@@

%\maketitle
\begin{abstract}
Embedded Systems Design often requires conflicting objectives to be
optimized with an appropriate choice of hardware/software parameters .
Interdependencies among these parameters can make this task even more
difficult, since an a-priori knowledge of them would  be required to
develop an analytical model of the system. In this work we present PS,
a multiobjective exploration strategy that introduces the notion of
Parameters Space Representation. After a detailed formal description
of the algorithm and its concepts, we show a hardware/software
exploration case study. Qualitative and quantitative comparisons of PS
against a well-know multiobjective genetic approach demonstrate that,
while not outperforming it in terms of dominance, the proposed
approach can trade the uniformity and granularity qualities of the
solutions found for obtaining larger Pareto sets, thus representing a
further choice for designer when objective constrains allow it.
\end{abstract}

>>>>

\usepackage{subfigure}
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{balance}
\usepackage{float}
\usepackage{threeparttable}

@@

%------------------------------------------------------------------------------
\newcommand{\figR}[1]{Fig.~\ref{fig:#1}}
\newcommand{\figLC}[2]{
        \caption{#2}
        \label{fig:#1}
        %\vspace{-10pt}
}
\newcommand{\secL}[1]{\label{sec:#1}}
\newcommand{\secR}[1]{Sec.~\ref{sec:#1}}

\newcommand{\defL}[1]{\label{def:#1}}
\newcommand{\defR}[1]{Def.~\ref{def:#1}}

@@

%\maketitle
\begin{abstract}
Embedded Systems Design often requires conflicting objectives to be
optimized with an appropriate choice of hardware/software parameters .
Interdependencies among these parameters can make this task even more
difficult, since an a-priori knowledge of them would  be required to
develop an analytical model of the system. In this work we present PS,
a multiobjective exploration \comment{metterei algorithm anziche' strategy, che mi sembra troppo vago e non fa capire bene} strategy that introduces the notion of
Parameters Space Representation. After a detailed formal description
of the algorithm and its concepts, we show a hardware/software
exploration case study. Qualitative and quantitative comparisons of PS
against a well-know multiobjective genetic approach demonstrate that,
while not outperforming it in terms of dominance, the proposed
approach can trade the uniformity and granularity qualities of the
solutions found for obtaining larger Pareto sets, thus representing a
further choice for designer when objective constrains allow it.
\end{abstract}
